
This seed project is aligned with the topic entitled {\em sensing, advanced
analytics, and/or responses to optimize embedded systems}.  Through our new
models and methods for Embodied AI, we will systematically integrate and
optimize resource, and accuracy-aware machine learning methods to enable much
smaller, more power efficient, and more reliable implementation of autonomous
aerial vehicles compared to what is possible using conventional design methods.
We will demonstrate these approaches through the design of smaller quadrotors
and new nano-quadrotors capable of monitoring the environment and performing
delivery tasks in a local environment. Their advantages over larger quadrotors
are due to safety, agility and power efficiency. Smaller quadrotors are safer
to humans, other beings and the environment, inflicting no or minimal damage
upon collision. They are more agile because  of smaller moment
of inertia, which makes their reaction to environmental factors faster.

The proposed seed grant would allow  jump
starting collaboration between the two PIs, Bhattacharyya and Ferm\"{u}ller,
and linking this collaboration to technical problems  of relevance to
Northrop Grumman.  The PIs both have significant experience in
interdisciplinary, multi-investigator collaborations, but have not worked together
before on joint research projects. The seed grant would enable development of
preliminary results that would allow the PIs to more effectively 
pursue funding opportunities at relevant agencies. Furthermore, research in collaboration with Northrop Grumman will help to strengthen the
proposals and research in terms of impact to industry and defense.




